---
title:
output: 
  revealjs::revealjs_presentation:
    theme: night
    transition: slide
    highlight: espresso
---

## <divs> R for BC Stats </divs>
<img src = "www/RStudioLogo.png">

## Introduction to R

R has an extensive history as a tool for statistical analysis in academia. Due to relatively recent development efforts such as RStudio and "tidyverse," R is now more approachable and user friendly than ever before. 

## Benefits of R to BC Stats

> - Highly customizable data visualization; beyond the capabilities of Excel
> - One stop shop for projects; allows for data manipulation and tabulation, regression analysis, and results sharing in an integrated fashion
> - Requires significant investment of time and effort initially, but promotes the creation of easily reproducible workflows
> - Enables collaboration on projects both with individuals inside and outside of the organization
> - High degree of compatibility with Microsoft Office suite and other software packages currently in use

## Sample tasks well suited for R

> - Run SQL-like queries on an imported dataset
> - Produce various types of graphs and charts, with the option of very precise controls on the aesthetics 
> - Easily generate maps highlighting numerical attributes across different economic regions
> - Generate PDF reports in batch
> - Create dynamic web applications to present survey results

## {data-background-video="www/migrationApp.webm" data-background-video-loop="true"}

## Current projects

> - WES Engagement Migration Survey app
> - BC Public Service Career Survey app
> - Career survey batch summary reports
> - Re-usable presentation templates
> - Data visualization for various reports
> - Census survey batch profile maps
> - <img src = "www/censusMaps.gif">

## Other sample usages

Enter data and summary tables

```{r}
summary(cars)
```

## Easily embed plots within slide decks

```{r, echo=FALSE}
plot(cars)
```

